Turkey Hemorrhagic Enteritis Virus transcriptome profiling

### 2023-03-29 README.Rmd
Edit project README.Rmd and revert DAG graphs to SVG

- `AGAT`
- `Hisat2`
- `StringTie`
- `r R.version.string`
- `tidyverse`(v.`r packageVersion("tidyverse")`)
- `rmarkdown`(v.`r packageVersion("rmarkdown")`)
- `Snakemake`
- `zsh shell`
- See `environment.yml` for `conda env` dependencies

>>>>

- `AGAT`
- `Hisat2`
- `StringTie`
- ``r R.version.string``
- `tidyverse`(v.`r packageVersion("tidyverse")`)
- `rmarkdown`(v.`r packageVersion("rmarkdown")`)
- `Snakemake`
- `zsh shell`
- See `environment.yml` for `conda env` dependencies
